\documentclass{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{cite}
\begin{document}
\lstset{language=Java}
\title{CS317 homework 5}
\author{Yuchen Hou}
\maketitle
\section{Language to automaton}
Figure Attached.
\section{Automaton to language}
\begin{align*}
R(i,j,k) &= R(i,j,k-1) + R(i,k,k-1)R(k,k,k-1)^*R(k,j,k-1)\\
L(M) &= R(1,2,2) = R(1,2,1) + R(1,2,1)R(2,2,1)^*R(2,2,1)\\
R(1,2,1) &= R(1,2,0) + R(1,1,0)R(1,1,0)^*R(1,2,0)\\
R(2,2,1) &= R(2,2,0) + R(2,1,0)R(1,1,0)^*R(1,2,0)\\
R(1,1,0) &= (a + \lambda)\\
R(1,2,0) &= b\\
R(2,1,0) &= b\\
R(2,2,0) &= (c + \lambda)\\
R(1,2,1) &= b + (a + \lambda)(a + \lambda)^*b\\
R(2,2,1) &= (c + \lambda) + b(a + \lambda)^*b\\
L(M) &= b + (a + \lambda)(a + \lambda)^*b + (b + (a + \lambda)(a +
\lambda)^*b)((c + \lambda) + b(a + \lambda)^*b)^*((c + \lambda) + b(a +
\lambda)^*b)\\
\end{align*}
\section{Pumping Lemma}
Proof by contradiction with assumption L is regular. Let i be the integer in the
pumping lemma. Pick $z = 0^i1^i$. $\vert z \vert > i \land z \in L$. From the
lemma, z = uvw, $\vert uv \vert \leq i \land \vert v \vert \geq 1$. Therefore, u
and v contain only 0's. From the lemma, $y = uvvw \in L$. But y contains more
0's than 1's. This is a contradiction since y should contain less (or equal) 0's
than 1's, according to the definition of L.
Thus L is not regular.
\section{Pumping lemma}
Proof by contradiction with assumption L is regular. Let i be the integer in
the pumping lemma. Pick $z = a^ib(a^ib)^Ra^ib$. $\vert z \vert > i \land z \in
L$. From the lemma, z = uvw, $\vert uv \vert \leq i \land \vert v \vert \geq 1
\land \vert w \vert < 4i$. Therefore, u and v contain only a's but w contains
a's and b's. From the lemma, $y = uv^{1000000i}w \in L$ and the first half of y
are all a's. Also, $y = xx^Rx$, so x contains only a's, so u contains only a's.
So the pumping process removed those b's! This is a contradiction.
Thus L is not regular.
\section{Regular language}
\subsection{}
\subsubsection{Statement}
Not regular.
\subsubsection{Proof}
Proof by contradiction with assumption L is regular. Let i be the integer in the
pumping lemma. Pick $z = 0^i1^i0^{2i}$. $\vert z \vert > i \land z \in L$. From
the lemma, z = uvw, $\vert uv \vert \leq i \land \vert v \vert \geq 1$.
Therefore, u and v contain only 0's and $w = 0^j1^i0^{2i}$. From
the lemma, by pumping 0's, $y = uv^{2i}w \in L$. In y, there are more than 2i
0's before those 1's and 2i 0's after those 1's. This is a contradiction since the number
of 0's before 1's should be less than the number of 0's after 1's, according to
the definition of L.
Thus L is not regular.
\subsection{}
\subsubsection{Statement}
Regular.
\subsubsection{Proof}
This language has a regular expression $r = 0^4(00)^*$.
Thus L is regular.
\subsection{}
\subsubsection{Statement}
Regular.
\subsubsection{Proof}
Regular language $K = \{(0+1)^*\} $ is a subset of L (when x = $\lambda$).
However, as $\Sigma = \{0, 1\}$. L must also be a subset of K.
So L = K and L is regular.
\subsection{}
\subsubsection{Statement}
Not regular.
\subsubsection{Proof}
Proof by contradiction with assumption L is regular. Let i be the number in
pumping lemma. Pick $z = 0^{i+1}1^i \in L$. From the lemma, $z = uvw \land \vert
uv \vert \leq i \land \vert v \vert \geq 1$, so u and v contain only 0's. From
the lemma, $y = uw = 0^j1^i \in L$, where $j \leq i$. This is a contradiction
since j should be greater than i, according to the definition of L.
\end{document}